Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-20 manuscript.tex
New abstract

The Hydrogen Epoch of Reionization Array (HERA) is a staged experiment that uses the unique properties of the 21\,cm line from neutral hydrogen to probe the Epoch of Reionization (EOR). During this epoch, roughly 0.3 - 1 billion years after the Big Bang, the first galaxies and black holes heated and reionized the early Universe. Direct observation of the large scale structure of reionization and its evolution with time will have a profound impact on our understanding of the birth of the first galaxies and black holes, their influence on the intergalactic medium (IGM), and cosmology.  This paper will provide an overview of the project and describe the design of the system, moving from a science overview to requirements, design and status.

\section{Introduction}
The Hydrogen Epoch of Reionization Array (HERA; http://reionization.org) is a staged experiment to use the redshifted 21\,cm line
of neutral hydrogen to characterize our Cosmic Dawn, from
the formation of the first stars and black holes $\sim0.1~$Gyr after the Big
Bang ($z\sim30$) through the full reionization of the intergalactic medium
(IGM) $\sim1~$Gyr later ($z\sim6$).  By directly observing the large scale
structure of the primordial IGM as it is heated and reionized, HERA complements
other probes, adding transformative capabilities for
understanding the astrophysics and fundamental cosmology of our early universe.
Taking advantage of a new understanding of bright foreground systematics, HERA's
purpose-built radio
interferometer is optimized to deliver high signal-to-noise measurements of
redshifted 21\,cm emission to detect and characterize the Epoch of Reionization (EOR).

>>>>

The Hydrogen Epoch of Reionization Array (HERA) is a staged experiment
optimized to measure 21 cm emission from the primordial
intergalactic medium (IGM) throughout cosmic reionization ($z=6-12$), with
support for exploring earlier stages of our Cosmic Dawn ($z\sim30$).  During these
epochs, early stars and black holes heat and ionize the IGM, introducing
fluctuations in 21 cm emission.  HERA aims to characterize the evolution of the 21 cm
power spectrum in detail to constrain the timing and morphology of
reionization, the properties of the first galaxies, the evolution of
large-scale structure, and the early sources of heating in the IGM.  
The full HERA instrument will be a
350-element interferometer in South Africa consisting of 14-m parabolic dishes observing from 50 to 250 MHz.
Currently, 19 dishes have been deployed on site and are being commissioned.

In this paper, we summarize HERA's scientific context and provide forecasts for
its key science results.  After reviewing the current state of the art in
foreground mitigation, we use the delay-spectrum technique to
motivate high-level performance requirements for the HERA instrument.  Next,
we present the HERA instrument design, along with the subsystem specifications that
ensure that HERA meets its performance requirements.  Finally, we summarize the schedule
and status of the project.  We conclude by suggesting that, given the realities of foreground
contamination, current-generation 21 cm instruments are approaching their sensitivity limits.
HERA is designed to bring both the
sensitivity and the precision to deliver its primary science on the basis of
proven foreground filtering techniques, while developing new subtraction
techniques to unlock new capabilities.  The result will be a major step toward
realizing the widely recognized scientific potential of 21 cm cosmology.

\section{Introduction}

The Hydrogen Epoch of Reionization Array (HERA; http://reionization.org) is a staged experiment to use the redshifted 21\,cm line
of neutral hydrogen to characterize our Cosmic Dawn, from
the formation of the first stars and black holes $\sim0.1~$Gyr after the Big
Bang ($z\sim30$) through the full reionization of the intergalactic medium
(IGM) $\sim1~$Gyr later ($z\sim6$).  By directly observing the large scale
structure of the primordial IGM as it is heated and reionized, HERA complements
other probes, adding transformative capabilities for
understanding the astrophysics and fundamental cosmology of our early universe.
Taking advantage of a new understanding of bright foreground systematics, HERA's
purpose-built radio
interferometer is optimized to deliver high signal-to-noise measurements of
redshifted 21\,cm emission to detect and characterize the Epoch of Reionization (EOR).
